### 2022-01-24 input/experiments.tex
reworked figures

\begin{figure}
  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.eps}
  \caption{\label{fig:complexity}Overhead of dynamic consistent partitioning
    using \NAME.}

@@

\begin{figure}
  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.eps}
  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters connected by a long distance link.}
\end{figure}

@@

\begin{figure*}
  \subfloat {
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
  }
  \hspace{5pt}
  \subfloat {
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.eps}
  }
  \caption{\label{fig:europe-ases}Traffic overhead and indexes
    maintained by \NAME and its extension \NAMEC in an Edge
    infrastructure comprising 40 interconnected autonomous systems of
    1157 \processes spanning across Europe~\cite{knight2011internet}}
\end{figure*}

@@

\begin{asparadesc}
  \item[Overall,] these experiments highlight the scalability of \NAME
    and \NAMEC in dynamic networks such as Edge infrastructures. Next
    Section reviews state-of-the-art approaches designed to index
    content in geo-distributed infrastructures.
\end{asparadesc}

% \TODO{Overall + transition.}

>>>>

\begin{figure}
  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf}
  \caption{\label{fig:complexity}Overhead of dynamic consistent partitioning
    using \NAME.}

@@

\begin{figure}
  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters connected by a long distance link.}
\end{figure}

@@

\begin{figure*}
  \subfloat {
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
  }
  \hspace{5pt}
  \subfloat {
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.pdf}
  }
  \caption{\label{fig:europe-ases}Traffic overhead and indexes
    maintained by \NAME and its extension \NAMEC in an Edge
    infrastructure comprising 40 interconnected autonomous systems of
    1157 \processes spanning across Europe~\cite{knight2011internet}}
\end{figure*}

@@

\begin{asparadesc}
  \item[Overall,] these experiments highlight the scalability of \NAME
    and \NAMEC in dynamic networks such as Edge infrastructures. Next
    Section reviews state-of-the-art approaches that can index content
    in geo-distributed infrastructures.
\end{asparadesc}
